## Using plotmath for graph labels.

(Here's the ".Rmd" file that produced what you're reading: [label.Rmd](label.Rmd).)

Here are several plots with successively harder labels using text, the value of a variable, and `plotmath` notation.

### First, an easy text title:
```{r}
curve(sqrt(x), from=0, to=4, main="Ugly plain text: y = sqrt(x)")
```

### Second, an easy title using `plotmath` and `expression`, but no text:
```{r}
curve(sqrt(x), from=0, to=4, main=expression(sqrt(x)))
```

### Third, combine `plotmath` and text:

* In the context of "`expression()`", the asterisk, "`*`", indicates joining
```{r}
curve(sqrt(x), from=0, to=4, main=expression("The square root of n: " * sqrt(n)))
```

### Fourth, combine text and the value of a variable:
```{r}
n = 2
curve(sqrt(x), from=0, to=4, main=paste(sep="", "The square root of ", n, " is ", sqrt(n)))
```

### Fifth, combine plotmath and the value of a variable:

* In `plotmath`, `sqrt(2)` indicates $\sqrt{2}$
* `bquote()` is like `expression()` in that it facilitates plotmath, but it also allows the inclusion of the value of a variable:
    + "`.()`" indicates, in the context of "`bquote()`", that its argument should be evaluated, so
        - "`.(n)`" indicates the value of the "`n`" variable, that is, 2
        - "`.(sqrt(n))`" indicates the value of "`sqrt(n)`", that is, 1.414...
* here "`bquote()`" combines the previous two elements into a title
```{r}
n = 2
curve(sqrt(x), from=0, to=4, main=bquote(sqrt(.(n))==.(sqrt(n))))
```

### Sixth and finally, combine text, plotmath, and the value of a variable:
```{r}
n = 2
curve(sqrt(x), from=0, to=4, main=bquote("The square root of " * .(n) * " is " * sqrt(.(n))==.(sqrt(n))))
```
