---
title: "STAT 327 Homework 3"
output: html_document
---

We'll grade your homework by

* opening your "hw3.Rmd" file in RStudio
* clicking "Knit HTML"
* reading the HTML output
* reading your "hw3.Rmd"

You should write R code anywhere you see an empty R code chunk. You
should write English text anywhere you see "..."; please surround it
with doubled asterisks (`**...**`) so that it will show up as boldface
and be easy for us to find.

Include reasonable labels (titles, axis labels, legends, etc.) with
each of your graphs.

Name: ...

Email: ...

We'll use data on housing values in suburbs of Boston. They are in an
R package called "MASS." (An R package is a collection of code,
data, and documentation. "MASS" refers to the book "Modern Applied
Statistics with S." R developed from the earlier language, S.) The
MASS package comes with the default R installation, so it's already on
your computer.  However, it's not loaded into your R session by
default. So we'll load it via the `require()` command (there's nothing
for you to do here):

```{r}
require("MASS")
```

Run `?Boston` (outside this R Markdown document) to read the help page for the `Boston` data frame.

Convert the `chas` variable to a factor with labels "off" and "on" (referring to the Charles river).

```{r}
bos <- Boston
bos$chas <- factor(bos$chas, levels = c(0, 1), labels = c("on", "off"))
```

How many rows are in the Boston data frame? How many columns?

```{r}
str(bos)
```
**14 columns and 506 rows.**

What does a row represent?

**Each row represents a neighborhood.**

What does a column represent?

**Column represents a variable of interest.**

Make a density plot (with rug) of tax rates.

```{r}
plot(density(bos$tax))
rug(bos$tax)
```

Describe the shape of the distribution of tax rates.

**Bimodal**

Note that the distribution shape doesn't make sense in light of the rug representation of the data. Make a histogram of the tax rates.

```{r}
hist(bos$tax)
```

Why is the second peak of the density plot so large? In what way is the rug representation of the data inadequate? Write a line or two of code to figure it out, and then explain it.

```{r}
length(bos$tax[bos$tax > 600])
```
**Rug doesnt show that there are 137 houses that have a tax rate over 600 which is why the density has a peak there.**

Make a barplot of "chas".

```{r}
barplot(table(bos$chas))
```

How many neighborhoods are on the Charles river?

```{r}
length(bos$chas[bos$chas == "on"])
```

Make a single graph consisting of three plots: 

* a scatterplot of "nox" on the y-axis vs. "dis" on the x-axis 
* a (vertical) boxplot of "nox" left of the scatterplot's y-axis
* a (horizontal) boxplot of "dis" below the scatterplot's x-axis

Hint: use `layout()` with a 4x4 matrix, using the top-right 3x3 corner
for the scatterplot, leaving the bottom-left 1x1 corner blank, and
using the other parts for the boxplots.

(An optional challenge, worth 0 extra credit points: remove the axis
and plot border from each boxplot.)

```{r, fig.width=7, fig.height=7}
m <- matrix(data = c(2, 1, 1, 1, 2, 1, 1, 1, 2, 1, 1, 1, 0, 3, 3, 3), nrow = 4, ncol = 4, byrow = TRUE)
layout(m)
plot(x = bos$dis, y = bos$nox)
boxplot(bos$nox)
boxplot(bos$dis, horizontal = TRUE)
```

Look into the highest-crime neighborhood by making a single graph of one column of three rows:

* Find the row number, r, of the neighborhood with the highest "crim".
* Make a density plot of "crim". Include a rug to show the data.
* Add a red circle at (x, y) = (max crime rate, 0) to make this maximum crime rate stand out.
* Make a density plot with rug of "medv", adding a red circle at (x, y) = (medv[r], 0) to see what medv corresponds to the highest crime rate.
* Repeat the last step for "ptratio".

```{r}
par(mfrow = c(3,1))
bos[which.max(bos$crim) , ]
plot(density(bos$crim))
rug(bos$crim)
points(x = bos$crim[which.max(bos$crim)], y = 0, col = "red", pch = 19)
plot(density(bos$medv))
rug(bos$medv)
points(x = bos$medv[which.max(bos$crim)], y = 0, pch = 19, col = "red")
plot(density(bos$ptratio))
rug(bos$ptratio)
points(x = bos$ptratio[which.max(bos$crim)], y = 0, pch = 19, col = "red")
```

What do you notice about the ptratio and medv for the highest-crime neighborhood?

...
