# STAT 327 Group work on Optimization

Please write the names and email addresses of your group members.
Here's an example:

* Name / email (@wisc.edu only): John Gillett / jgillett@wisc.edu

* Name / email (@wisc.edu only): ...
* Name / email (@wisc.edu only): ...
* Name / email (@wisc.edu only): ...
* Name / email (@wisc.edu only): ...
* Name / email (@wisc.edu only): ...
* Name / email (@wisc.edu only): ...

# Part 1: One-dimensional optimization

Graph the object's altitude vs. time.

```{r}
drag <- function(t) {
  g = 9.81 
  z0 = 100 
  v0 = 55
  m = 80
  c = 15
  return(abs(z0 + (((m/c)*(v0 + ((m*g)/c))*(1 - exp(-((c/m)*t))))) - (((m*g)/c)*t)))
}
curve(drag, from = 0, to = 11.61085)
```

Find the time at which the object strikes the ground.

```{r}
drag <- function(z0, m, c, v0, g, t) {
  return(abs(z0 + (((m/c)*(v0 + ((m*g)/c))*(1 - exp(-((c/m)*t))))) - (((m*g)/c)*t)))
}
min <- optimize(drag, c(0,12),g = 9.81, z0 = 100, v0 = 55, m = 80, c = 15)
min$minimum
```

Find the object's maximum height.

```{r}
drag <- function(z0, m, c, v0, g, t) {
  return(-(z0 + (((m/c)*(v0 + ((m*g)/c))*(1 - exp(-((c/m)*t))))) - (((m*g)/c)*t)))
}
max <- optimize(drag, c(0,12),g = 9.81, z0 = 100, v0 = 55, m = 80, c = 15)
-max$objective
```

Find the time at which the object reaches its maximum height.

```{r}
drag <- function(z0, m, c, v0, g, t) {
  return(-(z0 + (((m/c)*(v0 + ((m*g)/c))*(1 - exp(-((c/m)*t))))) - (((m*g)/c)*t)))
}
max <- optimize(drag, c(0,12),g = 9.81, z0 = 100, v0 = 55, m = 80, c = 15)
max$minimum
```

# Part 2: Multi-dimensional optimization

Implement `gradient.descent()`.

```{r}
poll.conc <- function(x, y) {
  return(7.9 + (0.13*x) + (0.21*y) - (0.05*(x^2)) - (0.016*(y^2)) - (0.007*x*y))
}
```

Graph the concentration.

Use `gradient.descent()` to find the peak.

Use `optim()` with `method=Nelder-Mead` to find the peak.

Use `optim()` with `method=BFGS` to find the peak.

How many calls did `optim()` make in each case? Which method would you
expect to be faster?